rtorf An R package for processing atmospheric greenhouse gas observations in NOAA's ObsPack

### 2024-07-10 README.Rmd
remove cols arguemnt from obs_Read_nc

```{r}
df <- obs_read_nc(index = index,
                  categories = "tower-insitu")

@@

```{r, eval = T}
master <- df3
master$timeUTC <- as.character(master$timeUTC)
fwrite(master, 
       file =  paste0(tempdir(), "/tower_insitu_2020.txt"),
       sep = " ")
```

>>>>

```{r}
df <- obs_read_nc(
  index = index,
  categories = "tower-insitu")

@@

```{r, eval = T}
master <- df4
master$timeUTC <- as.character(master$timeUTC)
fwrite(master, 
       file =  paste0(tempdir(), "/tower_insitu_2020.txt"),
       sep = " ")
```

### 2024-07-10 paper_elsevier/paper_elsevier.Rmd
remove cols arguemnt from obs_Read_nc

```{r install, eval = F}
remotes::install_github("ibarraespinosa/rtorf")
library(rtorf)
```

@@

https://github.com/ibarraespinosa/rtorf/tree/main/rscripts

@@

```{r flow, echo = FALSE, message=FALSE, fig.cap="Methane observations (ppb) by towers-insitu", out.height="50%", out.width="100%"}
knitr::include_graphics("flow/Slide1.PNG")
```

>>>>

```{r install, eval = F}
remotes::install_github("noaa-gml/rtorf")
library(rtorf)
```

@@

https://github.com/noaa-gml/rtorf/tree/main/rscripts

@@
